Comunicações Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2015-05-05 tese/section01.tex
almost reviewed section 2
quase a roçar as 16 paginas

@@

\ac{WebRTC} defines three main \ac{API}s: GetUserMedia, PeerConnection and DataChannel.

\begin{itemize}
  \item \textbf{GetUserMedia} allows from the browser to access to camera, microphone and device screen.

@@

\ac{WebRTC}'s \textit{Data Channel} is built on top of \ac{SCTP}, which is secured by \ac{DTLS}. A \textit{Data Channel} has one incoming stream and one outgoing stream, providing bidirectional communication. Each data channel direction can be tweaked for reliable or unreliable transmission, the same can be done for order delivery. A priority can also be defined for improving the quality of service for a particular stream compared to another.

>>>>

\begin{figure}[H]
	\begin{center}
		\centering
		\includegraphics[width=0.6\textwidth]{figures/nat.png}

	\caption{Network Address Translation}
	\end{center}
\end{figure}

@@

{\color{magenta} [check the coverage of this stack]}

\ac{WebRTC} defines three main \ac{API}s: MediaStream, PeerConnection and DataChannel.

\begin{itemize}
  \item \textbf{MediaStream} allows from the browser to access to camera, microphone and device screen.

@@

\begin{figure}[H]
	\begin{center}
		\centering
		\includegraphics[width=0.6\textwidth]{figures/basic_protocols.png}

	\caption{Overview of transport protocols}
	\end{center}
\end{figure}

\ac{WebRTC}'s \textit{DataChannel} is built on top of \ac{SCTP}, which is encapsulated by \ac{DTLS}. \ac{DTLS} encapsulation provides confidentiality, authentication and integrity over the transfered data. A \textit{Data Channel} has one incoming stream and one outgoing stream, providing bidirectional communication. Each data channel direction can be tweaked for reliable or unreliable transmission, the same can be done for order delivery and priority which can also be defined for improving the quality of service for a particular stream compared to another.

\ac{WebRTC}'s \textit{MediaStream} is built on top of \ac{SRTP}, which requires an external mechanism for key exchange. \ac{DTLS} keys are negotiated on handshake in order to achieve a secure connection. The new keys derived from \ac{DTLS} handshake are seized for \ac{SRTP} encryption, the remaining communications are done through \ac{UDP} without using \ac{DTLS}.
